\documentclass[11pt]{custom-style}
\usepackage[NoDate
% ,LabelsAligned
]{currvita}

\providecommand*\email[1]{\href{mailto:#1}{#1}}
% \AtBeginDocument{\addtolength{\cvlabelwidth}{-15mm}}
\usepackage{etaremune}

\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}


\begin{document}
\begin{cv}{Curriculum Vit\ae{} of Stanislav Dashevskyi}
  \begin{cvlist}{Contact Information}
    \item 31 Porte de France\\
        L-4360 Esch-sur-Alzette\\
        Luxembourg
    \item \textit{+352 661 388049}
      \item \email{stdashevsky@gmail.com}
  \end{cvlist}

  \begin{cvlist}{Research Interests}
  \item Software Security, Software Vulnerabilities, Security
    Security of Software Supply Chain
  \end{cvlist}

  \begin{cvlist}{Skills}
  \item Programming (Java, Python), System administration (Linux, Docker), Web application development (ASP.NET, node.js), Mobile (Android), Statistical software packages (R, Matlab, scikit-learn, understanding of basic machine learning algorithms).
  \end{cvlist}

  \begin{cvlist}{Education}
  \item[2017] Ph.D., Computer Science - Software Security,
    \href{http://www.unitn.it/en}{University of Trento}, Trento, Italy
    \begin{labeling}{Supervisor:}
    \item[Thesis:] \emph{Security Assessment of Open Source
        Third-parties Applications}
    \item[Supervisors:] \href{http://disi.unitn.it/~massacci/}
      {Prof. Dr. Fabio Massacci} and \href{https://www.sabetta.com/}
      {Dr. Antonino Sabetta}
    \end{labeling}
  \item[2010] BSc. MSc., Computer Science - Automation and Control
    Systems, \href{http://www.nmu.org.ua/en/}{National Mining
      University}, Dnipropetrovsk, Ukraine.
    \begin{labeling}{Supervisor:}
    \item[Thesis:] \emph{Modelling an Automated Temperature Control
        System for Multichannel Iron Ore Roasting Machines and
        Optimizing Natural Gas Consumption Parameters.}
    \item[Supervisor:]
      \href{http://aks.nmu.org.ua/en/Dep_ACS/Tkachev.php}
      {Prof. Dr. Tkachov V.V.}
    \end{labeling}
  \end{cvlist}

  \begin{cvlist}{Training and Internships}
  \item[2017] FOSAD summer school on Foundations of Security Analysis and Design (Bertinoro, Italy).
  \item[2016] SECENTIS winter school on Security and Trust of Next Generation Enterprise Information Systems (Trento, Italy).
  \item[2015] Internship at SAP on Security Assessment of Open Source Software Components, supervised by Dr. \href{https://www.brucker.ch}{Achim D. Brucker} (Karlsruhe, Germany).
  \item[2014] Marktoberdorf summer school on Dependable Software Systems Engineering (Marktoberdorf, Germany).
  \item[2010] Internship at the University of Reutlingen on developing an automated management system for a fleet of electric vehicles, supervised by Prof. Dr. Gerhard Gruhler (Reutlingen, Germany).
  \end{cvlist}  

  \begin{cvlist}{Research Experience}
  \item[Since Sep. 2017] \href{https://wwwfr.uni.lu/snt}{Interdisciplinary Centre for Security, Reliability and Trust (SnT)},\\
    \href{http://satoss.uni.lu/}{SaToSS research group},\\
    University of Luxembourg\\
    Supervisor:
    \href{http://satoss.uni.lu/members/sjouke/}{Prof. Dr. Sjouke Mauw}
  \end{cvlist}

  \begin{cvlist}{Work Experience}
  \item[Jan. 2012 - Aug 2013] QA Engineer at \href{https://www.sitecore.com/company}{Sitecore} (Ukrainian office)\\
      Software test automation, working on creating company's own software testing frameworks, 
      continuous integration tasks and security testing.
  \end{cvlist}
  
  \begin{cvlist}{Scientific Projects}
  \item \href{http://www.secentis.eu/}{SECENTIS:} Security and
    Trust of Next Generation Enterprise Information Systems.
  \end{cvlist}
  
  \begin{cvlist}{Awards}
  \item[2010] \href{https://www.bw-stipendium.de/en/home/}{Baden-W{\"u}rttemberg
      Scholarship}, Reutlingen, Germany
  \end{cvlist}

  \begin{cvlist}{Publications}
  \item[Journals]
    \begin{etaremune}
    \item \textbf{S. Dashevskyi}, A. D. Brucker, and F. Massacci. ``A
      Screening Test for Disclosed Vulnerabilities in FOSS
      Components''. Accepted for publication in IEEE Transactions on
      Software Engineering (TSE), 2018.
    \item \textbf{S. Dashevskyi}, D. R. dos Santos, F. Massacci, and
      A. Sabetta. ``TestREx: a Framework for Repeatable
      Exploits''. International Journal of Software Tools for
      Technology Transfer (STTT), 2017.
    \item V.H. Nguyen,\textbf{S. Dashevskyi}, and F. Massacci. ``An
      Automatic Method for Assessing the Versions Affected by a
      Vulnerability''. Empirical Software Engineering Journal (ESE),
      2016.
    \end{etaremune}
  \item[Conferences]
    \begin{etaremune}
    \item A. Pilgun, O. Gadyatskaya, \textbf{S. Dashevskyi},
      Y. Zhauniarovich, and A. Kushniarou. ``An Effective Android Code
      Coverage Tool''. CCS'2018 (DEMO).
    \item \textbf{S. Dashevskyi}, O. Gadyatskaya, A. Pilgun and
      Y. Zhauniarovich. ``The Influence of Code Coverage Metrics on
      Automated Testing Efficiency in Android''. CCS'2018 (POSTER).
    \item \textbf{S. Dashevskyi}, A. D. Brucker, and F. Massacci. ``On
      the Effort for Security Maintenance of Free and Open Source
      Components''. Presented at WEIS 2018, Innsbruck, AT.
    \item I. Pashchenko, \textbf{S. Dashevskyi}, and
      F. Massacci. ``DeltaBench: Differential Benchmark for Static
      Analysis Security Testing Tools''. In Proceedings of the
      International Symposium on Empirical Software Engineering and
      Measurement (ESEM), 2017.
    \item \textbf{S. Dashevskyi}, A. D. Brucker, and F. Massacci. ``On
      the Security Cost of Using a Free and Open Source Component in a
      Proprietary Product''. In Proceedings of the Engineering Secure
      Software and Systems Conference (ESSoS), 2016.
    \item \textbf{S. Dashevskyi}, D. R. Dos Santos, F. Massacci, and
      A. Sabetta. ``TestREx: a Testbed for Repeatable Exploits''. In
      Proceedings of the 7th USENIX Workshop on Cyber Security
      Experimentation and Test (USENIX CSET), 2014.
    \end{etaremune}
  \item[Patents]
    \begin{etaremune}
    \item A. D. Brucker, \textbf{S. Dashevskyi}. ``Vulnerability
      Analysis of Software Components'', US Patent App. 14/965,449,
      2017.
    \item A. Sabetta, L. Compagna, S. Ponta, \textbf{S. Dashevskyi},
      D.R. Dos Santos, and F. Massacci. ``Multi-Context Exploit Test
      Management''. US Patent App. 14/692,203, 2016.
    \end{etaremune}
  \item[Book Chapters]
    \begin{etaremune}
    \item L. ben Othmane, A. D. Brucker, \textbf{S. Dashevskyi}, and
      P. Tsalovski, ``Empirical research for software security:
      foundations and experience''. In, L. ben Othmane, M.G. Jaatun,
      and E. Weippl, Eds. CRC Press, 2017, ch. ``An introduction to
      data analytics for software security''.
    \end{etaremune}
    \item[Talks]
      \begin{etaremune}
      \item A. D. Brucker, \textbf{S. Dashevskyi}, and F. Massacci,
        ``Using Third-party Components for Building an Application
        Might be More Dangerous than You Think!". OWASP AppSec Europe,
        2016.
        \href{https://www.brucker.ch/bibliography/download/2016/talk-brucker.ea-owasp-third-party-security-2016-2x2.pdf}{(Slides)}
        \href{https://www.youtube.com/watch?v=zUDaP0m-gFU&feature=youtu.be}{(Recording)}
    \item \textbf{S. Dashevskyi}, A. D. Brucker, and F. Massacci,
        ``A Screening Test for Disclosed Vulnerabilities in FOSS Components'', Journal-First presentation at ICSE 2019.
      \end{etaremune}
  \end{cvlist}

  \begin{cvlist}{Teaching Experience}
      \item[2019] Teaching assistant for the \href{http://satoss.uni.lu/courses/networksecurity/}{Network Security}] 
                Master course on network security offered by the University of Luxembourg.

       \item[2019] Teaching assistant for the \href{http://satoss.uni.lu/courses/sec-intro/}{Introduction to IT Security}
                Bachelor course on network security offered by the University of Luxembourg.

      \item[2018] Teaching assistant for the \href{http://satoss.uni.lu/courses/networksecurity/}{Network Security}] 
                Master course on network security offered by the University of Luxembourg.

      \item[2017] Teaching assistant for the \href{https://securitylab.disi.unitn.it/doku.php?id=ict_innovation}{ICT
          Innovation/Product Design and Development} Master course offered by the University of Trento.

      \item[2017] Teaching assistant for the
          \href{http://securitylab.disi.unitn.it/doku.php?id=course_on_offensive_technologies}{Offensive Technologies}
            Master course offered by the University of Trento.

      \item[2014] Teaching assistant for the
          \href{http://securitylab.disi.unitn.it/doku.php?id=course_on_offensive_technologies}{Offensive Technologies}
            Master course offered by the University of Trento.

  \end{cvlist}

\end{cv}
\end{document}
\endinput
